\bf Measuring background and systemic risk using financial time series

### 2015-06-04 srisk6.tex
pdj changes

\section{Systemic risk -- SRISK}\label{srisk}

@@

\section{Estimating background and systemic stress via simulation}\label{estimate}

@@

\section{Simulating future capital shortfall and market return}\label{simulate}

@@

 \begin{figure}[htbp]
\begin{center}
\label{default}
\includegraphics{figures/default.pdf}
\caption{Forecast one month ahead  Basel default probability (top panels), background stress (middle panels) and systemic stress (bottom panels) for  four major (left panel) and four minor (right panel)  banks from the beginning of 2003 through to end of 2014.  Note different scale on bottom two rows of panels.}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\label{muqs}
\includegraphics{figures/muqs.pdf}
\caption{Average  stresses and  total stresses.   Stress measurements are, left to right, $\mu$, $q$ and $s$, respectively.   The top row of panels measure for example (top left panel)  $\overline \mu_t$ and $\mu_t$ over time.    In the bottom row of panels  specific stresses are measured are against each other:  for example $\mu_t$ (vertical axis) versus $\overline\mu_t$ (horizontal axis).  In all cases there is no total stress until there is an appreciable level of average stress.  Systemic stress $\overline s_t$ appears to be the least diversifiable.}
\end{center}
\end{figure}

@@

System compliance is partially monitored with the system put $\overline p_t=\Exd(p_{it})$ and its stressed expectation $\Es(\overline p_t)$. However both quantities are before diversification and gives no indication of system resilience and as to how much risk can be diversified away. Basing a put on system wide aggregated debt and equity and comparing the same to $p_t$  gives at least some guidance.

@@

All model fits in this paper have been performed with the R language \citep{R-Development-Core-Team:2008aa} and in particular the rmgarch package described by \cite{ghalanos2012rmgarch}.  All other calculations were performed using the J language \citep{iverson2003j}.

\section{Proof of system put is less   than debt weighted average put}\label{proof}

$$
1-\e^{-\ell_{it}} = \frac{ \kappa d_{it} - (1-\kappa)w_{it}}{\kappa d_{it}}\cq \Ex_d (1-\e^{-\ell_{it}}) = \frac{\kappa d_t - (1-\kappa) w_t}{\kappa d_t} = 1-\e^{-\ell_t} \ ,
$$
and similarly if $-\ell_{it}$ is replaced by $\nu_{it}-\ell_{it}$.   Hence
$$
p_t\equiv |1-\e^{-\ell_t}|^+ \le \Ex_d (|1-\e^{-\ell_{it}}|^+)\equiv \overline p_t\ .
$$

@@

>>>>

\section{SRISK and systemic risk}\label{srisk}

@@

\section{Background and systemic stress via simulation}\label{estimate}

@@

\section{Forward capital shortfall and  return simulations}\label{simulate}

@@

 \begin{figure}[htbp]
\begin{center}
\includegraphics{figures/default.pdf}
\caption{Forecast one month ahead  Basel default probability (top panels), background stress (middle panels) and systemic stress (bottom panels) for  four major (left panel) and four minor (right panel)  banks from the beginning of 2003 through to end of 2014.  Note different scale on bottom two rows of panels.}\label{default}

\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics{figures/muqs.pdf}
\caption{Average  stresses and  total stresses.   Stress measurements are, left to right, $\mu$, $q$ and $s$, respectively.   The top row of panels measure for example (top left panel)  $\overline \mu_t$ and $\mu_t$ over time.    In the bottom row of panels  specific stresses are measured are against each other:  for example $\mu_t$ (vertical axis) versus $\overline\mu_t$ (horizontal axis).  In all cases there is no total stress until there is an appreciable level of average stress.  Systemic stress $\overline s_t$ appears to be the least diversifiable.}\label{muqs}
\end{center}
\end{figure}

@@

System compliance is partially monitored with the system put $\overline p_t=\Exd(p_{it})$ and its stressed expectation $\Es(\overline p_t)$. However both quantities are before diversification and give no indication of system resilience and as to how much risk can be diversified away. Basing a put on system wide aggregated debt and equity and comparing the same to $p_t$  gives at least some guidance.

@@

\section{Proof of system put is less   than debt weighted average put}\label{proof}
Since
$$
1-\e^{-\ell_{it}} = \frac{ \kappa d_{it} - (1-\kappa)w_{it}}{\kappa d_{it}}\cq \Ex_d (1-\e^{-\ell_{it}}) = \frac{\kappa d_t - (1-\kappa) w_t}{\kappa d_t} = 1-\e^{-\ell_t} \ ,
$$
and similarly if $-\ell_{it}$ is replaced by $\nu_{it}-\ell_{it}$.   Hence
$$
p_t\equiv |1-\e^{-\ell_t}|^+ \le \Ex_d (|1-\e^{-\ell_{it}}|^+)\equiv \overline p_t\ .
$$

@@

All model fits in this paper are performed with the R language \citep{R-Development-Core-Team:2008aa} and in particular the rmgarch package described by \cite{ghalanos2012rmgarch}.  All other calculations are done in the J language \citep{iverson2003j}.
